Classical density functional theory for the square-well liquid

### 2014-04-14 papers/square-well-liquid/paper.tex
make flat histogram mostly work (involved fixing bug in weight-handling in move_one_ball) Tested on darcy. Took 3:47.08.
added RDF plotting script Tested on MAPHost. Took 1:24.70.
minor changes to SW paper Tested on elliot. Took 0:19.75.

\fixme{DR -- Some notes are as follows:}

In Gil-Villegas' paper, HS and Dispersion are wrapped up into the
\textit{monomer} contribution, expressed in terms of energy densities
as:
\begin{align}
  f_\text{mono} = f_\text{HS} - \frac{\alpha^\text{VDW}n}{kT}
\end{align}
with $\alpha^\text{VDW}$ given by
\begin{align}
  \alpha^\text{VDW} &= 2\pi\epsilon\int_\sigma^\infty r^2\phi(r)\,dr \\
  \intertext{using reduced units of $x = r/\sigma$, we have}
  &= 2\pi\sigma^3\int_1^\infty x^2\phi(x)\,dx \\
  &= 3b^\text{VDW}\epsilon\int_1^\infty x^2\phi(x)\,dx
\end{align}
where $b^\text{VDW}$ is the van der Waals size parameter. It corresponds to the volume excluded by two spherical particles of volume $b$: $b^\text{VDW} = 4b = 4\left(\pi\sigma^3/6\right)$.
Then, the high-temp expansion is an expansion of the monomer term:
\begin{align}
  f_\text{mono} &= f_\text{HS} + \beta a_1 + \beta^2 a_2 + \cdots
\end{align}
\fixme{I'm not sure how to express this in terms of $F_\text{disp}[n]$ alone.}

The term $a_1$ is given by
\begin{align}
  a_1 &= -2\pi\rho_s\epsilon\int_\sigma^\infty r^2\phi(r)g^\text{HS}(r)\,dr \\
  &= -3\rho_sb^\text{VDW}\epsilon\int_1^\infty x^2\phi(x)g^\text{HS}(x)\,dx
\end{align}
If assume a random correlations between the particles' positions, for all distances, we have $g^\text{HS}(r) = 1$. This yields
\begin{align}
  a_1^\text{VDW} = -\rho_s\alpha^\text{VDW},
\end{align}
the van der Waals mean-field energy.

The second-order term is quite a bit more complicated; one must have
knowledge of higher-order correlation functions to determine
$a_2$. This term describes the response of the attractive energy due
to the compression of the fluid from the attractive well. Gil-Villegas
\emph{et al.} base their expression on an approximation by Barker and
Henderson\cite{barker1967-SW-perturbation}. \fixme{Gil-Villegas also
  cites 2 other Barker and Henderson papers, but I can't find one and
  the other doesn't seem relevant}. Barker and Henderson's
approximation considers fluctuations in the number of particles in the
potential well. In this way, the fluctuations in $a_2$ are related to the pressure and compressibility
of the liquid. Given pressure $P^\text{HS}$ and isothermal compressibility $K^\text{HS} = kT\left(\partial\rho_s/\partial P^\text{HS}\right)_T$, we have:
\begin{align}
  a_2 &= -\pi\rho_s\epsilon^2kT\int_0^\infty r^2\left[\phi(r)\right]^2\frac{\partial\rho_s g^\text{HS}(r)}{\partial P^\text{HS}}\,dr \\
  &= -\pi\rho_s\epsilon^2K^\text{HS}\frac{\partial}{\partial\rho_s}\left[\int_\sigma^\infty r^2\left[\phi(r)\right]^2\rho_s g^\text{HS}\,dr\right] \\
  &= \frac{1}{2}\epsilon K^\text{HS}\frac{\partial}{\partial\rho_s}\left[-3\rho_sb^\text{VDW}\epsilon\int_1^\infty x^2\left[\phi(x)\right]^2 g^\text{HS}(x)\,dx \right]
\end{align}

@@

\fixme{End of my comments --DR}

>>>>

\fixme{DRoth -- Some notes are as follows:}

In Gil-Villegas' paper, HS and Dispersion are wrapped up into the
\textit{monomer} contribution, expressed in terms of energy densities
as:
\begin{align}
  f_\text{mono} = f_\text{HS} - \frac{\alpha^\text{VDW}n}{kT}
\end{align}
with $\alpha^\text{VDW}$ given by
\begin{align}
  \alpha^\text{VDW} &= 2\pi\epsilon\int_\sigma^\infty r^2\phi(r)\,dr \\
  \intertext{using reduced units of $x = r/\sigma$, we have}
  &= 2\pi\sigma^3\int_1^\infty x^2\phi(x)\,dx \\
  &= 3b^\text{VDW}\epsilon\int_1^\infty x^2\phi(x)\,dx
\end{align}
where $b^\text{VDW}$ is the van der Waals size parameter. It corresponds to the volume excluded by two spherical particles of volume $b$: $b^\text{VDW} = 4b = 4\left(\pi\sigma^3/6\right)$.

Then, the high-temp expansion is an expansion of the monomer term:
\begin{align}
  f_\text{mono} &= f_\text{HS} + \beta a_1 + \beta^2 a_2 + \cdots
\end{align}
\fixme{I'm not sure how to express this in terms of $F_\text{disp}[n]$ alone.}

The term $a_1$ is given by
\begin{align}
  a_1 &= -2\pi\rho\epsilon\int_\sigma^\infty r^2\phi(r)g^\text{HS}(r)\,dr \\
  &= -3\rho b^\text{VDW}\epsilon\int_1^\infty x^2\phi(x)g^\text{HS}(x)\,dx
\end{align}
If assume a random correlations between the particles' positions, for all distances, we have $g^\text{HS}(r) = 1$. This yields
\begin{align}
  a_1^\text{VDW} = -\rho\alpha^\text{VDW},
\end{align}
the van der Waals mean-field energy.

The second-order term is quite a bit more complicated; one must have
knowledge of higher-order correlation functions to determine
$a_2$. This term describes the response of the attractive energy due
to the compression of the fluid from the attractive well. Gil-Villegas
\emph{et al.} base their expression on an approximation by Barker and
Henderson\cite{barker1967-SW-perturbation}. \fixme{Gil-Villegas also
  cites 2 other Barker and Henderson papers, but I can't find one and
  the other doesn't seem relevant}. Barker and Henderson's
approximation considers fluctuations in the number of particles in the
potential well. In this way, the fluctuations in $a_2$ are related to the pressure and compressibility
of the liquid. Given pressure $P^\text{HS}$ and isothermal compressibility $K^\text{HS} = kT\left(\partial\rho /\partial P^\text{HS}\right)_T$, we have:
\begin{align}
  a_2 &= -\pi\rho\epsilon^2kT\int_0^\infty r^2\left[\phi(r)\right]^2\frac{\partial\rho g^\text{HS}(r)}{\partial P^\text{HS}}\,dr \\
  &= -\pi\rho\epsilon^2K^\text{HS}\frac{\partial}{\partial\rho}\left[\int_\sigma^\infty r^2\left[\phi(r)\right]^2\rho g^\text{HS}\,dr\right] \\
  &= \frac{1}{2}\epsilon K^\text{HS}\frac{\partial}{\partial\rho}\left[-3\rho b^\text{VDW}\epsilon\int_1^\infty x^2\left[\phi(x)\right]^2 g^\text{HS}(x)\,dx \right]
\end{align}

@@

\fixme{End of my comments --DRoth}
